A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-11 doc/popl2013/intro.tex
intro

The important difference between Legion and the more static approaches
is that Legion allows region aliasing, but does so in a structured way that minimizes
runtime overheads.  The key observation is that
static alias analysis is hard, but dynamic analysis is very easy
and relatively cheap
when done at the granularity of regions instead of individual heap
locations.  Thus, Legion falls between fully static systems, such as
Sequoia and DPJ, and fully dynamic approaches such as transactional
memory.  Legion still has a significant static component; in
particular, the required privileges for function calls
and region
pointer dereferences are checked statically.  The dynamic alias checks
for independence are done at the granularity of regions and one check 
on a region
often serves to prove the independence of many subsequent uses of that region.
In contrast, because transactional memory has no mechanism
for grouping heap data into larger collections, it must test the
overlap between two sets of data on each individual memory access, which is
significantly more expensive.

>>>>

The important difference between Legion and the more static approaches
is that Legion allows region aliasing, but does so in a structured way that minimizes
runtime overheads.  The key observation is that
static alias analysis is hard, but dynamic analysis is very easy
and relatively cheap
when done at the granularity of regions instead of individual heap
locations.  Thus, Legion falls between fully static systems, such as
Sequoia and DPJ, and fully dynamic approaches such as transactional
memory.  Legion still has a significant static component; in
particular, the required privileges for function calls
and region
pointer dereferences are checked statically.  The dynamic alias checks
for independence are done at the granularity of regions and one check 
on a region
often serves to prove the independence of many subsequent uses of that region.
In contrast, because transactional memory has no mechanism
for grouping heap data into larger collections, it must test the
overlap between two sets of data on each individual memory location, which is
significantly more expensive.
